Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2013-01-14 chi2013-webbox.tex
Versus consistency fix

Once established, equivalent properties were examined, first, for naming inconsistencies.  Then, disregarding names, we examined whether the property's values were structurally compatible.  That is, if both values consisted of the same literal data type, or had one or more equivalent subfields, they were considered compatible.  Finally, we examined incompatibilities not covered by either naming or structural differences alone.  These \emph{modelling differences} arose from a variety of reasons, including, but not limited to, measurement unit inconsistencies, measurement method disagreements (e.g., dew point vs relative humidity), differences in scale and granularity, and mismatches in what was being modelled (``offer'' versus ``listing'').\looseness=-1

>>>>

Once established, equivalent properties were examined, first, for naming inconsistencies.  Then, disregarding names, we examined whether the property's values were structurally compatible.  That is, if both values consisted of the same literal data type, or had one or more equivalent subfields, they were considered compatible.  Finally, we examined incompatibilities not covered by either naming or structural differences alone.  These \emph{modelling differences} arose from a variety of reasons, including, but not limited to, measurement unit inconsistencies, measurement method disagreements (e.g., ``dew point'' versus ``relative humidity''), differences in scale and granularity, and mismatches in what was being modelled (e.g., ``offer'' versus ``listing'').\looseness=-1
